Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
comments

\subsection{Improved Algorithm for Online Rematching} \label{sec:k2}
In this section,
we present \RM,
 an algorithm for clusters of capacity $k=2$.
We interpret a~pair of nodes collocated in one cluster as a~``matched'' pair.
Hence,
the problem is an online variant of the maximal matching problem where
%a match is retractable.
%That is, 
a matched pair can separate in order to ``rematch'' with two other nodes.
Rematching is necessary for  maximizing intra-cluster communications,
which is dual \maciek{dual has specific meaning. Is it correct here? I think you meant "equivalent" here} to minimizing inter-cluster communications.
This is known as the  \emph{online rematching} 
problem and a~non-strict 7-competitive algorithm is already given by~\cite{repartition-disc},
in which the ratio comes with an additive factor $O(\alpha\ell^2)$.
We do not only improve upon their competitive ratio,
but also show that our ratio holds \emph{strictly}
(i.e., with no additive factor).
Our algorithm is slightly simpler than the one in~\cite{repartition-disc}, 
while our analysis is significantly  simpler and more concise,
thanks to the charging scheme we devise here.

>>>>

\subsection{Improved Algorithm for Online Rematching} \label{sec:k2}
In this section,
we present \RM,
 an algorithm for clusters of capacity $k=2$.
We interpret a~pair of nodes collocated in one cluster as a~``matched'' pair.
Hence,
the problem is an online variant of the maximal matching problem where
%a match is retractable.
%That is, 
a matched pair can separate in order to ``rematch'' with two other nodes.
Rematching is necessary for  maximizing intra-cluster communications,
which is dual \maciek{dual has specific meaning. Is it correct here? I think you meant "equivalent" here} to minimizing inter-cluster communications.
This is known as the  \emph{online rematching} 
problem and a~non-strict 7-competitive algorithm is already given by~\cite{repartition-disc},
in which the ratio comes with an additive factor $O(\alpha\ell^2)$.
We do not only improve upon their competitive ratio,
but also show that our ratio holds \emph{strictly}
(i.e., with no additive factor).
Our algorithm is slightly simpler than the one in~\cite{repartition-disc}, 
while our analysis is significantly  simpler and more concise,
thanks to the charging scheme we devise here \maciek{Way too strong. At best, analysis is slightly simpler. Just compare volumes and the notation needed.}.
